---
title: "Assignment #3"
output: html_document
---
# Project Info  
**January 28, 2021**  
**Author**: rbio1   
**Github Repository**: [rbio/432W3](https://github.com/rbio1/432W3)  

***

```{r setup, include=FALSE}
library(dplyr)
```  
Load the FallopiaData.csv from InputData folder using a relative path  
```{r}
FalloData<-read.csv("./InputData/FallopiaData.csv")
```
The following operations will:  

* Remove rows with ‘Total’ biomass < 60  
  + Using filter() 
* Reorder the columns so that they are in the order: ‘Total’, ‘Taxon’, ‘Senario’, ‘Nutrients’, and remove the other columns  
  + Using select()
* Make a new column TotalG, which converts the ‘Total’ column from mg to grams AND replace Total with TotalG, and add it to the dataset.  
  + Using transmute()
```{r}
FalloData<-FalloData %>%
  filter(Total>=60) %>%
  select(Total,Taxon,Scenario,Nutrients) %>%
  transmute(TotalG=Total/1000,Taxon,Scenario,Nutrients)
```
The data frame "FalloData" now consists of 45 observations of 4 variables  

***
The custom function 'ASOFun' will take two inputs from the user: 1. a vector of data to process (e.g. column from a data.frame object) and 2. a string that defines what calculation to perform.  

* if string #2 is "Average" then calculate the average value for the column named in vector #1  
* if string #2 is "Sum" then calculate the sum of values for the column named in vector #1
* if string #2 is "Observations" then count the number of observed values for the column named in vector #1
* if string #2 is anything else, then output an error to the user
```{r}
ASOFun<-function(Column,Command){
  if(Command=="Sum"){
    return(sum(Column))}
  if(Command=="Observations"){
    return(length(Column))}
  if(Command=="Average"){
    return(sum(Column)/length(Column))}
  else(return("Error:Check Input"))
}
```
The following code will count the total number of observations in the 'Taxon' column.
```{r}
ASOFun(FalloData$Taxon,"Observations")
```
The average TotalG for each of the two nutrient concentrations can be calculated by the custom function in cooperation with the *dplyr* operation "group_by"
```{r}
FalloData %>%
  group_by(Nutrients) %>%
  summarize(Mean=ASOFun(TotalG,"Average"))
```  

***
The new data frame is saved to a file in the Output folder  
```{r}
write.csv(FalloData,"./Output/WrangledData.csv")
```